---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# certificate

<!-- badges: start -->
[![R-CMD-check](https://github.com/forwards/certificate/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/forwards/certificate/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The **certificate** package is designed to help generate certificates for R 
courses.

## Installation

This package is not on CRAN.  You can install the package from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("forwards/certificate")
```

## Example

First load the package 

```{r load}
library(certificate)
```

Certificates can be generate for multiple participants at once. Here we specify 
a couple of fake names for illustration (generated with `charlatan::ch_name`):

```{r attendees}
attendees <- c("Marnie Dickinson", "Dr. Marlin Wilderman")
```

Then we specify the basic metadata of the workshop, which will be the same for 
all certificates

```{r workshop_metadata}
workshop <- "Package development workshop"
date <- as.Date("2018-01-01")
location <- "University of Lorraine"
```

The curriculum is a summary of the workshop contents. This should be specified 
in markdown format and it is easier to write this in a separate markdown file. 
An example is included in the **certificate** package.

```{r curriculum_chunk}
curriculum <- system.file("rmarkdown", "templates",
                          "workshop_certificate", "resources",
                          "default_workshop_contents.md", 
                          package = "certificate")
readLines(curriculum)
```
The last set of required information is about the certifying person and the 
certifying organization

```{r certifier}
certifier <- "Zaire Crooks"
credentials <- "Forwards teaching team member"
organization <- "Forwards, the R Foundation taskforce for women and other
under-represented groups"
organization_url <- "forwards.github.io/"
```

Now we can generate the certificates in a new directory, e.g.

```{r certificates}
dir <- "~/Desktop/certificates"
create_workshop_certificates(attendees, workshop, date, location,
                             curriculum, certifier, credentials,
                             organization, organization_url,
                             dir)
```

See `?create_workshop_certificate` for more detail on the arguments of this 
function, which allow customization of the wording, logo and colours, as well 
as the option to supply an image of a signature to place on the signature line.
